\textbf{Supporting Information:}

### 2021-01-06 Supplementary_material/Supp_Material.tex

\textbf{Figure S1.} Correlation matrix for all the different traits.

\textbf{Figure S2.} Total amount of pollen found for the different
treatments.

\textbf{Figure S3.} Pollen ratios for the different recipient species.

\textbf{Figure S4.} Pollen ratios for the different recipient species by
family.

\textbf{Figure S5.} Statistical comparison of pollen ratios by family as
pollen donor and recipient.

\textbf{Figure S6.} Violin plot of the reproductive biology of the
species.

Figure S7. Grouped effect sizes by family for each recipient species.

>>>>

\textbf{Table S9.} Phylogenetic signal and significance for all the
different traits.

\textbf{Figure S1}. Average number of pollen grains of recipient and
donor species per stigma with the 50:50 mix CP:HP pollen.

\textbf{Figure S2}. Average proportion (\%) of conspecific and
heterospecific pollen per stigma with the 50:50 mix CP:HP pollen.

\textbf{Figure S3}. Average proportion (\%) of heterospecific and
conspecific pollen per stigma and family with the 50:50 mix CP:HP
pollen.

\textbf{Figure S4}. Statistical comparison of the percentage of
heterospecific pollen with the 50:50 pollen mix by family.

\textbf{Figure S5}. Unipartite bidirectional network with asymmetrical
effect.

\textbf{Figure S6}. Correlation matrix for all the different traits.

\textbf{Figure S7}. Species reproductive biology.

\textbf{Figure S8}. Grouped effect sizes by family for each recipient
species.

\newpage

\begingroup\fontsize{10}{12}\selectfont

\begin{longtabu} to \linewidth {>{}l>{\raggedright}X>{\raggedright}X>{\raggedright}X}
\caption{\label{tab:unnamed-chunk-1}\textbf{Table S1.} Species names, common names, varieties and sources of the different seeds.}\\
\toprule
\textbf{Species} & \textbf{Common names} & \textbf{Varieties} & \textbf{Source}\\
\midrule
\endfirsthead
\caption[]{\textbf{Table S1.} Species names, common names, varieties and sources of the different seeds. \textit{(continued)}}\\
\toprule
\textbf{Species} & \textbf{Common names} & \textbf{Varieties} & \textbf{Source}\\
\midrule
\endhead

\endfoot
\bottomrule
\endlastfoot
\em{\cellcolor{gray!6}{Brassica oleracea}} & \cellcolor{gray!6}{Wild cabbage} & \cellcolor{gray!6}{Capitata} & \cellcolor{gray!6}{https://www.mrfothergills.com.au/}\\
\addlinespace
\em{Brassica rapa} & Pak choi & Chinensis & https://www.mrfothergills.com.au/\\
\addlinespace
\em{\cellcolor{gray!6}{Eruca sativa}} & \cellcolor{gray!6}{Rocket} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{https://www.mrfothergills.com.au/}\\
\addlinespace
\em{Sinapis alba} & White mustard &  & https://www.mrfothergills.com.au/\\
\addlinespace
\em{\cellcolor{gray!6}{Ipomoea aquatica}} & \cellcolor{gray!6}{Water spinach} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{https://www.theseedcollection.com.au/}\\
\addlinespace
\em{Ipomoea purpurea} & Morning glory &  & http://www.shaman-australis.com.au\\
\addlinespace
\em{\cellcolor{gray!6}{Capsicum annuum}} & \cellcolor{gray!6}{Capsicum} & \cellcolor{gray!6}{California Wonder} & \cellcolor{gray!6}{https://www.edenseeds.com.au}\\
\addlinespace
\em{Petunia integrifolia} & Petunia &  & https://www.dianeseeds.com/\\
\addlinespace
\em{\cellcolor{gray!6}{Solanum lycopersicum}} & \cellcolor{gray!6}{Tomato} & \cellcolor{gray!6}{Tommy Toe} & \cellcolor{gray!6}{https://www.mrfothergills.com.au/}\\
\addlinespace
\em{Solanum melongena} & Eggplant & Little Fingers & https://www.4seasonsseeds.com.au/\\*
\end{longtabu}

\endgroup{}

\begin{landscape}

\begin{table}

\caption{\label{tab:unnamed-chunk-2}\textbf{Table S2.} Average values of the trait measurements for each plant species. Sample sizes are provided on the methods section. Detailed information of how pollen:ovule ratio, selfing rate and SI index were calculated is available in the plant functional traits section from the methods. The raw data can be found on the online repository provided within this manuscript.}
\centering
\resizebox{\linewidth}{!}{
\fontsize{6}{8}\selectfont
\begin{tabu} to \linewidth {>{}l>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X}
\toprule
\textbf{Species} & \textbf{Pollen size $\mu$m} & \textbf{Pollen grains per anther} & \textbf{Ovule number} & \textbf{Pollen:ovule ratio} & \textbf{Stigma area $\mu$m$^{2}$} & \textbf{Stigma length (mm)} & \textbf{Stigma width (mm)} & \textbf{Style length (mm)} & \textbf{Style width (mm)} & \textbf{Ovary length (mm)} & \textbf{Ovary width (mm)} & \textbf{Selfing rate} & \textbf{SI index}\\
\midrule
\em{\cellcolor{gray!6}{Brassica oleracea}} & \cellcolor{gray!6}{27.72} & \cellcolor{gray!6}{42033} & \cellcolor{gray!6}{29} & \cellcolor{gray!6}{8696.48} & \cellcolor{gray!6}{0.62} & \cellcolor{gray!6}{0.53} & \cellcolor{gray!6}{0.88} & \cellcolor{gray!6}{2.32} & \cellcolor{gray!6}{0.65} & \cellcolor{gray!6}{5.93} & \cellcolor{gray!6}{1.11} & \cellcolor{gray!6}{0.0} & \cellcolor{gray!6}{0.00}\\
\addlinespace
\em{Brassica rapa} & 25.35 & 7133 & 26 & 1646.08 & 0.36 & 0.37 & 0.73 & 1.08 & 0.52 & 3.53 & 0.88 & 0.0 & 0.00\\
\addlinespace
\em{\cellcolor{gray!6}{Capsicum annuum}} & \cellcolor{gray!6}{32.46} & \cellcolor{gray!6}{30761} & \cellcolor{gray!6}{241} & \cellcolor{gray!6}{765.83} & \cellcolor{gray!6}{1.06} & \cellcolor{gray!6}{0.72} & \cellcolor{gray!6}{1.18} & \cellcolor{gray!6}{3.24} & \cellcolor{gray!6}{1.06} & \cellcolor{gray!6}{3.15} & \cellcolor{gray!6}{5.80} & \cellcolor{gray!6}{0.8} & \cellcolor{gray!6}{0.64}\\
\addlinespace
\em{Eruca versicaria} & 24.95 & 22151 & 24 & 5537.75 & 0.35 & 0.73 & 0.67 & 6.60 & 0.73 & 4.42 & 0.94 & 0.1 & 0.02\\
\addlinespace
\em{\cellcolor{gray!6}{Ipomoea aquatica}} & \cellcolor{gray!6}{70.10} & \cellcolor{gray!6}{858} & \cellcolor{gray!6}{4} & \cellcolor{gray!6}{1072.50} & \cellcolor{gray!6}{3.26} & \cellcolor{gray!6}{1.43} & \cellcolor{gray!6}{2.25} & \cellcolor{gray!6}{19.44} & \cellcolor{gray!6}{0.45} & \cellcolor{gray!6}{2.38} & \cellcolor{gray!6}{1.42} & \cellcolor{gray!6}{0.6} & \cellcolor{gray!6}{0.75}\\
\addlinespace
\em{Ipomoea purpurea} & 97.59 & 654 & 6 & 545.00 & 2.27 & 1.24 & 1.88 & 28.23 & 0.58 & 1.06 & 1.57 & 1.0 & 2.74\\
\addlinespace
\em{\cellcolor{gray!6}{Petunia integrifolia}} & \cellcolor{gray!6}{24.74} & \cellcolor{gray!6}{34657} & \cellcolor{gray!6}{220} & \cellcolor{gray!6}{787.66} & \cellcolor{gray!6}{1.17} & \cellcolor{gray!6}{0.80} & \cellcolor{gray!6}{1.32} & \cellcolor{gray!6}{14.65} & \cellcolor{gray!6}{0.45} & \cellcolor{gray!6}{3.13} & \cellcolor{gray!6}{1.77} & \cellcolor{gray!6}{0.9} & \cellcolor{gray!6}{0.26}\\
\addlinespace
\em{Sinapis alba} & 33.59 & 3507 & 6 & 3507.00 & 0.55 & 0.63 & 0.91 & 3.62 & 0.77 & 1.98 & 1.07 & 0.7 & 1.12\\
\addlinespace
\em{\cellcolor{gray!6}{Solanum lycopersicum}} & \cellcolor{gray!6}{22.00} & \cellcolor{gray!6}{28915} & \cellcolor{gray!6}{92} & \cellcolor{gray!6}{1885.76} & \cellcolor{gray!6}{0.09} & \cellcolor{gray!6}{0.19} & \cellcolor{gray!6}{0.35} & \cellcolor{gray!6}{6.47} & \cellcolor{gray!6}{0.31} & \cellcolor{gray!6}{1.16} & \cellcolor{gray!6}{1.13} & \cellcolor{gray!6}{0.7} & \cellcolor{gray!6}{0.48}\\
\addlinespace
\em{Solanum melongena} & 25.18 & 166989 & 1010 & 992.01 & 1.14 & 0.96 & 1.33 & 11.33 & 0.94 & 4.02 & 3.55 & 1.0 & 1.45\\
\bottomrule
\end{tabu}}
\end{table}

\end{landscape}

\newpage

\begin{table}

\caption{\label{tab:unnamed-chunk-3}\textbf{Table S3.} Average recipient and donor pollen grains per stigma with the 50:50 mix CP:HP pollen for the subset of 20 counts (3 replicates per treatment).}
\centering
\resizebox{\linewidth}{!}{
\fontsize{10}{12}\selectfont
\begin{tabu} to \linewidth {>{}l>{}l>{\raggedleft}X>{\raggedleft}X}
\toprule
\textbf{Recipient species} & \textbf{Donor species} & \textbf{Recipient pollen grains} & \textbf{Donor pollen grains}\\
\midrule
\em{\cellcolor{gray!6}{C. annuum}} & \em{\cellcolor{gray!6}{I. purpurea}} & \cellcolor{gray!6}{258} & \cellcolor{gray!6}{11}\\
\addlinespace
\em{E. sativa} & \em{I. purpurea} & 1308 & 8\\
\addlinespace
\em{\cellcolor{gray!6}{B. oleracea}} & \em{\cellcolor{gray!6}{I. purpurea}} & \cellcolor{gray!6}{90} & \cellcolor{gray!6}{20}\\
\addlinespace
\em{B. rapa} & \em{I. purpurea} & 193 & 2\\
\addlinespace
\em{\cellcolor{gray!6}{S. melongena}} & \em{\cellcolor{gray!6}{I. aquatica}} & \cellcolor{gray!6}{64} & \cellcolor{gray!6}{26}\\
\addlinespace
\em{P. integrifolia} & \em{I. aquatica} & 23 & 20\\
\addlinespace
\em{\cellcolor{gray!6}{S. lycopersicum}} & \em{\cellcolor{gray!6}{I. aquatica}} & \cellcolor{gray!6}{56} & \cellcolor{gray!6}{10}\\
\addlinespace
\em{S. alba} & \em{I. aquatica} & 1617 & 19\\
\addlinespace
\em{\cellcolor{gray!6}{I. purpurea}} & \em{\cellcolor{gray!6}{S. melongena}} & \cellcolor{gray!6}{138} & \cellcolor{gray!6}{362}\\
\addlinespace
\em{S. alba} & \em{S. melongena} & 3054 & 1096\\
\addlinespace
\em{\cellcolor{gray!6}{E. sativa}} & \em{\cellcolor{gray!6}{P. integrifolia}} & \cellcolor{gray!6}{621} & \cellcolor{gray!6}{321}\\
\addlinespace
\em{B. rapa} & \em{S. lycopersicum} & 1114 & 246\\
\addlinespace
\em{\cellcolor{gray!6}{I. aquatica}} & \em{\cellcolor{gray!6}{C. annuum}} & \cellcolor{gray!6}{35} & \cellcolor{gray!6}{85}\\
\addlinespace
\em{B. oleracea} & \em{C. annuum} & 281 & 209\\
\addlinespace
\em{\cellcolor{gray!6}{I. purpurea}} & \em{\cellcolor{gray!6}{E. sativa}} & \cellcolor{gray!6}{27} & \cellcolor{gray!6}{216}\\
\addlinespace
\em{S. melongena} & \em{E. sativa} & 1837 & 2231\\
\addlinespace
\em{\cellcolor{gray!6}{P. integrifolia}} & \em{\cellcolor{gray!6}{B. oleracea}} & \cellcolor{gray!6}{332} & \cellcolor{gray!6}{376}\\
\addlinespace
\em{I. aquatica} & \em{S. alba} & 42 & 170\\
\addlinespace
\em{\cellcolor{gray!6}{C. annuum}} & \em{\cellcolor{gray!6}{S. alba}} & \cellcolor{gray!6}{304} & \cellcolor{gray!6}{450}\\
\addlinespace
\em{S. lycopersicum} & \em{B. rapa} & 164 & 208\\
\bottomrule
\end{tabu}}
\end{table}

\newpage

\begin{table}

\caption{\label{tab:unnamed-chunk-4}\textbf{Table S4.} Results of the test of hand cross-pollination, hand self-pollination, spontaneous selfing and apomixis for all species. The values provided are the seed:ovule ratios in percentage.}
\centering
\resizebox{\linewidth}{!}{
\fontsize{10}{12}\selectfont
\begin{tabu} to \linewidth {>{}l>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X}
\toprule
\textbf{Species} & \textbf{Hand cross-pollination} & \textbf{Hand self-pollination} & \textbf{Spontaneous selfing} & \textbf{Apomixis}\\
\midrule
\em{\cellcolor{gray!6}{Brassica oleracea}} & \cellcolor{gray!6}{32.07} & \cellcolor{gray!6}{0.00} & \cellcolor{gray!6}{0.00} & \cellcolor{gray!6}{0}\\
\addlinespace
\em{Brassica rapa} & 44.97 & 0.00 & 0.00 & 0\\
\addlinespace
\em{\cellcolor{gray!6}{Capsicum annuum}} & \cellcolor{gray!6}{80.00} & \cellcolor{gray!6}{56.47} & \cellcolor{gray!6}{19.34} & \cellcolor{gray!6}{0}\\
\addlinespace
\em{Eruca sativa} & 23.75 & 0.42 & 0.00 & 0\\
\addlinespace
\em{\cellcolor{gray!6}{Ipomoea aquatica}} & \cellcolor{gray!6}{40.00} & \cellcolor{gray!6}{30.00} & \cellcolor{gray!6}{20.00} & \cellcolor{gray!6}{0}\\
\addlinespace
\em{Ipomoea purpurea} & 31.67 & 86.67 & 31.67 & 0\\
\addlinespace
\em{\cellcolor{gray!6}{Petunia integrifolia}} & \cellcolor{gray!6}{80.16} & \cellcolor{gray!6}{24.77} & \cellcolor{gray!6}{0.00} & \cellcolor{gray!6}{0}\\
\addlinespace
\em{Sinapis alba} & 41.67 & 48.33 & 5.00 & 15\\
\addlinespace
\em{\cellcolor{gray!6}{Solanum lycopersium}} & \cellcolor{gray!6}{85.65} & \cellcolor{gray!6}{41.20} & \cellcolor{gray!6}{68.48} & \cellcolor{gray!6}{0}\\
\addlinespace
\em{Solanum melongena} & 60.48 & 74.87 & 21.56 & 0\\
\bottomrule
\end{tabu}}
\end{table}

\begin{landscape}

\begin{table}

\caption{\label{tab:unnamed-chunk-5}\textbf{Table S5.} Summary of the heterospecific pollen impacts from the linear models on each pollen recipient species. The category of “yes” represents a significant effect of the pollen donor (columns) on the recipient species (rows) and the category of “no” represents a lack of significant seed set reduction in comparison with the control treatment. Significance was tested for each species by comparing the different 50-50 CP-HP pollen treatments with the control treatment of hand cross-pollination with conspecific pollen.}
\centering
\resizebox{\linewidth}{!}{
\fontsize{6}{8}\selectfont
\begin{tabu} to \linewidth {>{}l>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedright\arraybackslash}p{1.5cm}>{\raggedright}X>{\raggedright}X}
\toprule
\em{} & \em{Brassica oleracea} & \em{Brassica rapa} & \em{Eruca sativa} & \em{Sinapis alba} & \em{Ipomoea aquatica} & \em{Ipomoea purpurea} & \em{Capsicum annuum} & \em{Petunia integrifolia} & \em{Solanum lycopersicum} & \em{Solanum melongena} & \em{$\%$ of significant effect}\\
\midrule
\em{\cellcolor{gray!6}{B. oleracea}} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{Yes} & \cellcolor{gray!6}{Yes} & \cellcolor{gray!6}{Yes} & \cellcolor{gray!6}{Yes} & \cellcolor{gray!6}{Yes} & \cellcolor{gray!6}{Yes} & \cellcolor{gray!6}{Yes} & \cellcolor{gray!6}{Yes} & \cellcolor{gray!6}{Yes} & \cellcolor{gray!6}{100}\\
\addlinespace
\em{B. rapa} & No &  & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & 88.9\\
\addlinespace
\em{\cellcolor{gray!6}{E. sativa}} & \cellcolor{gray!6}{Yes} & \cellcolor{gray!6}{No} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{No} & \cellcolor{gray!6}{Yes} & \cellcolor{gray!6}{No} & \cellcolor{gray!6}{No} & \cellcolor{gray!6}{No} & \cellcolor{gray!6}{No} & \cellcolor{gray!6}{No} & \cellcolor{gray!6}{22.2}\\
\addlinespace
\em{S. alba} & No & Yes & No &  & Yes & Yes & Yes & No & No & No & 44.4\\
\addlinespace
\em{\cellcolor{gray!6}{I. aquatica}} & \cellcolor{gray!6}{Yes} & \cellcolor{gray!6}{Yes} & \cellcolor{gray!6}{Yes} & \cellcolor{gray!6}{Yes} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{Yes} & \cellcolor{gray!6}{Yes} & \cellcolor{gray!6}{Yes} & \cellcolor{gray!6}{Yes} & \cellcolor{gray!6}{Yes} & \cellcolor{gray!6}{100}\\
\addlinespace
\em{I. purpurea} & No & No & Yes & No & No &  & Yes & No & Yes & No & 33.3\\
\addlinespace
\em{\cellcolor{gray!6}{C. annuum}} & \cellcolor{gray!6}{Yes} & \cellcolor{gray!6}{Yes} & \cellcolor{gray!6}{No} & \cellcolor{gray!6}{Yes} & \cellcolor{gray!6}{No} & \cellcolor{gray!6}{Yes} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{Yes} & \cellcolor{gray!6}{Yes1} & \cellcolor{gray!6}{Yes} & \cellcolor{gray!6}{77.8}\\
\addlinespace
\em{P. integrifolia} & Yes & No & No & Yes & Yes & Yes & No &  & Yes & Yes & 67.7\\
\addlinespace
\em{\cellcolor{gray!6}{S. lycopersicum}} & \cellcolor{gray!6}{No} & \cellcolor{gray!6}{Yes} & \cellcolor{gray!6}{Yes} & \cellcolor{gray!6}{Yes} & \cellcolor{gray!6}{Yes} & \cellcolor{gray!6}{Yes} & \cellcolor{gray!6}{Yes} & \cellcolor{gray!6}{Yes} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{Yes} & \cellcolor{gray!6}{88.9}\\
\addlinespace
\em{S. melongena} & No & Yes & Yes & No & Yes & Yes & Yes & No & No &  & 55.6\\
\addlinespace
\em{\cellcolor{gray!6}{}} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{$\bar{X}=67.8$}\\
\bottomrule
\end{tabu}}
\end{table}

\end{landscape}

\clearpage

\begingroup\fontsize{7}{9}\selectfont

\begin{longtable}[t]{>{}lrrrr}
\caption{\label{tab:unnamed-chunk-6}\textbf{Table S6.} Results of the linear models conducted to test the effect of heterospecific pollen with the 50-50 CP-HP pollen treatments. We conducted 10 different linear models (M1, M2, M3, M4, M5, M6, M7 M8, M9 and M10) where the effect of the different 9 pollen donors was compared with the control treatment of hand cross pollination with conspecific pollen for each recipient species (intercept). The first species on the row names are the pollen recipient species and the second species the pollen donor species. Each treatment is compared with the control or reference treatment that is indicated with the recipient species names and the intercept term between parentheses.}\\
\toprule
\textbf{ } & \textbf{Estimates} & \textbf{Standard error} & \textbf{t-value} & \textbf{{\textit{P}}-value}\\
\midrule
\em{\cellcolor{gray!6}{M1 Petunia integrifolia - (Intercept)}} & \cellcolor{gray!6}{4.63} & \cellcolor{gray!6}{0.49} & \cellcolor{gray!6}{9.36} & \cellcolor{gray!6}{0.00}\\
\addlinespace
\em{M1 Petunia integrifolia - Brassica oleracea} & -1.84 & 0.81 & -2.27 & 0.03\\
\addlinespace
\em{\cellcolor{gray!6}{M1 Petunia integrifolia - Brassica rapa}} & \cellcolor{gray!6}{-0.97} & \cellcolor{gray!6}{0.81} & \cellcolor{gray!6}{-1.19} & \cellcolor{gray!6}{0.24}\\
\addlinespace
\em{M1 Petunia integrifolia - Capsicum annuum} & 0.78 & 0.81 & 0.96 & 0.34\\
\addlinespace
\em{\cellcolor{gray!6}{M1 Petunia integrifolia - Eruca vesicaria}} & \cellcolor{gray!6}{-0.91} & \cellcolor{gray!6}{0.81} & \cellcolor{gray!6}{-1.12} & \cellcolor{gray!6}{0.26}\\
\addlinespace
\em{M1 Petunia integrifolia - Ipomoea aquatica} & -3.18 & 0.81 & -3.92 & 0.00\\
\addlinespace
\em{\cellcolor{gray!6}{M1 Petunia integrifolia - Ipomoea purpurea}} & \cellcolor{gray!6}{-4.21} & \cellcolor{gray!6}{0.81} & \cellcolor{gray!6}{-5.19} & \cellcolor{gray!6}{0.00}\\
\addlinespace
\em{M1 Petunia integrifolia - Sinapis alba} & -2.99 & 0.81 & -3.69 & 0.00\\
\addlinespace
\em{\cellcolor{gray!6}{M1 Petunia integrifolia - Solanum lycopersicum}} & \cellcolor{gray!6}{-2.40} & \cellcolor{gray!6}{0.81} & \cellcolor{gray!6}{-2.96} & \cellcolor{gray!6}{0.00}\\
\addlinespace
\em{M1 Petunia integrifolia - Solanum melongena} & -2.66 & 0.81 & -3.27 & 0.00\\
\addlinespace
\em{\cellcolor{gray!6}{M2 Solanum lycopersicum - (Intercept)}} & \cellcolor{gray!6}{4.39} & \cellcolor{gray!6}{0.24} & \cellcolor{gray!6}{18.54} & \cellcolor{gray!6}{0.00}\\
\addlinespace
\em{M2 Solanum lycopersicum - Brassica oleracea} & -0.47 & 0.41 & -1.14 & 0.26\\
\addlinespace
\em{\cellcolor{gray!6}{M2 Solanum lycopersicum - Brassica rapa}} & \cellcolor{gray!6}{-2.74} & \cellcolor{gray!6}{0.41} & \cellcolor{gray!6}{-6.67} & \cellcolor{gray!6}{0.00}\\
\addlinespace
\em{M2 Solanum lycopersicum - Capsicum annuum} & -4.39 & 0.41 & -10.71 & 0.00\\
\addlinespace
\em{\cellcolor{gray!6}{M2 Solanum lycopersicum - Eruca vesicaria}} & \cellcolor{gray!6}{-2.97} & \cellcolor{gray!6}{0.41} & \cellcolor{gray!6}{-7.25} & \cellcolor{gray!6}{0.00}\\
\addlinespace
\em{M2 Solanum lycopersicum - Ipomoea aquatica} & -4.13 & 0.41 & -10.06 & 0.00\\
\addlinespace
\em{\cellcolor{gray!6}{M2 Solanum lycopersicum - Ipomoea purpurea}} & \cellcolor{gray!6}{-3.80} & \cellcolor{gray!6}{0.41} & \cellcolor{gray!6}{-9.27} & \cellcolor{gray!6}{0.00}\\
\addlinespace
\em{M2 Solanum lycopersicum - Petunia integrifolia} & -1.82 & 0.41 & -4.44 & 0.00\\
\addlinespace
\em{\cellcolor{gray!6}{M2 Solanum lycopersicum - Sinapis alba}} & \cellcolor{gray!6}{-3.72} & \cellcolor{gray!6}{0.41} & \cellcolor{gray!6}{-9.08} & \cellcolor{gray!6}{0.00}\\
\addlinespace
\em{M2 Solanum lycopersicum - Solanum melongena} & -1.84 & 0.41 & -4.49 & 0.00\\
\addlinespace
\em{\cellcolor{gray!6}{M3 Solanum melongena - (Intercept)}} & \cellcolor{gray!6}{6.34} & \cellcolor{gray!6}{0.70} & \cellcolor{gray!6}{9.09} & \cellcolor{gray!6}{0.00}\\
\addlinespace
\em{M3 Solanum melongena - Brassica oleracea} & -0.67 & 0.99 & -0.68 & 0.50\\
\addlinespace
\em{\cellcolor{gray!6}{M3 Solanum melongena - Brassica rapa}} & \cellcolor{gray!6}{-4.33} & \cellcolor{gray!6}{0.99} & \cellcolor{gray!6}{-4.39} & \cellcolor{gray!6}{0.00}\\
\addlinespace
\em{M3 Solanum melongena - Capsicum annuum} & -2.33 & 0.99 & -2.36 & 0.02\\
\addlinespace
\em{\cellcolor{gray!6}{M3 Solanum melongena - Eruca vesicaria}} & \cellcolor{gray!6}{-3.12} & \cellcolor{gray!6}{0.99} & \cellcolor{gray!6}{-3.16} & \cellcolor{gray!6}{0.00}\\
\addlinespace
\em{M3 Solanum melongena - Ipomoea aquatica} & -6.34 & 0.99 & -6.43 & 0.00\\
\addlinespace
\em{\cellcolor{gray!6}{M3 Solanum melongena - Ipomoea purpurea}} & \cellcolor{gray!6}{-2.71} & \cellcolor{gray!6}{0.99} & \cellcolor{gray!6}{-2.74} & \cellcolor{gray!6}{0.01}\\
\addlinespace
\em{M3 Solanum melongena - Petunia integrifolia} & -1.43 & 0.99 & -1.45 & 0.15\\
\addlinespace
\em{\cellcolor{gray!6}{M3 Solanum melongena - Sinapis alba}} & \cellcolor{gray!6}{-1.11} & \cellcolor{gray!6}{0.99} & \cellcolor{gray!6}{-1.12} & \cellcolor{gray!6}{0.26}\\
\addlinespace
\em{M3 Solanum melongena - Solanum lycopersicum} & -0.84 & 0.99 & -0.86 & 0.39\\
\addlinespace
\em{\cellcolor{gray!6}{M4 Capsicum annuum - (Intercept)}} & \cellcolor{gray!6}{4.59} & \cellcolor{gray!6}{0.52} & \cellcolor{gray!6}{8.78} & \cellcolor{gray!6}{0.00}\\
\addlinespace
\em{M4 Capsicum annuum - Brassica oleracea} & -1.80 & 0.74 & -2.43 & 0.02\\
\addlinespace
\em{\cellcolor{gray!6}{M4 Capsicum annuum - Brassica rapa}} & \cellcolor{gray!6}{-2.51} & \cellcolor{gray!6}{0.74} & \cellcolor{gray!6}{-3.39} & \cellcolor{gray!6}{0.00}\\
\addlinespace
\em{M4 Capsicum annuum - Eruca vesicaria} & -0.63 & 0.74 & -0.85 & 0.40\\
\addlinespace
\em{\cellcolor{gray!6}{M4 Capsicum annuum - Ipomoea aquatica}} & \cellcolor{gray!6}{-1.36} & \cellcolor{gray!6}{0.74} & \cellcolor{gray!6}{-1.84} & \cellcolor{gray!6}{0.07}\\
\addlinespace
\em{M4 Capsicum annuum - Ipomoea purpurea} & -4.00 & 0.74 & -5.41 & 0.00\\
\addlinespace
\em{\cellcolor{gray!6}{M4 Capsicum annuum - Petunia integrifolia}} & \cellcolor{gray!6}{-4.59} & \cellcolor{gray!6}{0.74} & \cellcolor{gray!6}{-6.21} & \cellcolor{gray!6}{0.00}\\
\addlinespace
\em{M4 Capsicum annuum - Sinapis alba} & -3.63 & 0.74 & -4.92 & 0.00\\
\addlinespace
\em{\cellcolor{gray!6}{M4 Capsicum annuum - Solanum lycopersicum}} & \cellcolor{gray!6}{-1.52} & \cellcolor{gray!6}{0.74} & \cellcolor{gray!6}{-2.06} & \cellcolor{gray!6}{0.04}\\
\addlinespace
\em{M4 Capsicum annuum - Solanum melongena} & -3.29 & 0.74 & -4.46 & 0.00\\
\addlinespace
\em{\cellcolor{gray!6}{M5 Brassica oleracea - (Intercept)}} & \cellcolor{gray!6}{1.99} & \cellcolor{gray!6}{0.22} & \cellcolor{gray!6}{8.98} & \cellcolor{gray!6}{0.00}\\
\addlinespace
\em{M5 Brassica oleracea - Brassica rapa} & -1.37 & 0.31 & -4.35 & 0.00\\
\addlinespace
\em{\cellcolor{gray!6}{M5 Brassica oleracea - Capsicum annuum}} & \cellcolor{gray!6}{-0.87} & \cellcolor{gray!6}{0.31} & \cellcolor{gray!6}{-2.76} & \cellcolor{gray!6}{0.01}\\
\addlinespace
\em{M5 Brassica oleracea - Eruca vesicaria} & -1.92 & 0.31 & -6.13 & 0.00\\
\addlinespace
\em{\cellcolor{gray!6}{M5 Brassica oleracea - Ipomoea aquatica}} & \cellcolor{gray!6}{-1.91} & \cellcolor{gray!6}{0.27} & \cellcolor{gray!6}{-7.04} & \cellcolor{gray!6}{0.00}\\
\addlinespace
\em{M5 Brassica oleracea - Ipomoea purpurea} & -1.99 & 0.31 & -6.35 & 0.00\\
\addlinespace
\em{\cellcolor{gray!6}{M5 Brassica oleracea - Petunia integrifolia}} & \cellcolor{gray!6}{-1.64} & \cellcolor{gray!6}{0.31} & \cellcolor{gray!6}{-5.21} & \cellcolor{gray!6}{0.00}\\
\addlinespace
\em{M5 Brassica oleracea - Sinapis alba} & -1.57 & 0.31 & -4.99 & 0.00\\
\addlinespace
\em{\cellcolor{gray!6}{M5 Brassica oleracea - Solanum lycopersicum}} & \cellcolor{gray!6}{-1.47} & \cellcolor{gray!6}{0.31} & \cellcolor{gray!6}{-4.70} & \cellcolor{gray!6}{0.00}\\
\addlinespace
\em{M5 Brassica oleracea - Solanum melongena} & -1.61 & 0.31 & -5.12 & 0.00\\
\addlinespace
\em{\cellcolor{gray!6}{M6 Brassica rapa - (Intercept)}} & \cellcolor{gray!6}{2.37} & \cellcolor{gray!6}{0.19} & \cellcolor{gray!6}{12.49} & \cellcolor{gray!6}{0.00}\\
\addlinespace
\em{M6 Brassica rapa - Brassica oleracea} & -0.54 & 0.29 & -1.89 & 0.06\\
\addlinespace
\em{\cellcolor{gray!6}{M6 Brassica rapa - Capsicum annuum}} & \cellcolor{gray!6}{-1.42} & \cellcolor{gray!6}{0.29} & \cellcolor{gray!6}{-4.94} & \cellcolor{gray!6}{0.00}\\
\addlinespace
\em{M6 Brassica rapa - Eruca vesicaria} & -2.37 & 0.29 & -8.24 & 0.00\\
\addlinespace
\em{\cellcolor{gray!6}{M6 Brassica rapa - Ipomoea aquatica}} & \cellcolor{gray!6}{-1.92} & \cellcolor{gray!6}{0.29} & \cellcolor{gray!6}{-6.67} & \cellcolor{gray!6}{0.00}\\
\addlinespace
\em{M6 Brassica rapa - Ipomoea purpurea} & -2.26 & 0.29 & -7.86 & 0.00\\
\addlinespace
\em{\cellcolor{gray!6}{M6 Brassica rapa - Petunia integrifolia}} & \cellcolor{gray!6}{-2.37} & \cellcolor{gray!6}{0.29} & \cellcolor{gray!6}{-8.24} & \cellcolor{gray!6}{0.00}\\
\addlinespace
\em{M6 Brassica rapa - Sinapis alba} & -2.37 & 0.29 & -8.24 & 0.00\\
\addlinespace
\em{\cellcolor{gray!6}{M6 Brassica rapa - Solanum lycopersicum}} & \cellcolor{gray!6}{-1.88} & \cellcolor{gray!6}{0.29} & \cellcolor{gray!6}{-6.55} & \cellcolor{gray!6}{0.00}\\
\addlinespace
\em{M6 Brassica rapa - Solanum melongena} & -2.37 & 0.29 & -8.24 & 0.00\\
\addlinespace
\em{\cellcolor{gray!6}{M8 Eruca sativa - (Intercept)}} & \cellcolor{gray!6}{1.34} & \cellcolor{gray!6}{0.35} & \cellcolor{gray!6}{3.80} & \cellcolor{gray!6}{0.00}\\
\addlinespace
\em{M8 Eruca sativa - Brassica oleracea} & -1.34 & 0.50 & -2.69 & 0.01\\
\addlinespace
\em{\cellcolor{gray!6}{M8 Eruca sativa - Brassica rapa}} & \cellcolor{gray!6}{0.66} & \cellcolor{gray!6}{0.50} & \cellcolor{gray!6}{1.32} & \cellcolor{gray!6}{0.19}\\
\addlinespace
\em{M8 Eruca sativa - Capsicum annuum} & -0.27 & 0.50 & -0.55 & 0.58\\
\addlinespace
\em{\cellcolor{gray!6}{M8 Eruca sativa - Ipomoea aquatica}} & \cellcolor{gray!6}{0.87} & \cellcolor{gray!6}{0.50} & \cellcolor{gray!6}{1.75} & \cellcolor{gray!6}{0.08}\\
\addlinespace
